Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-13 MUSES_vs_BYOD_solutions.tex
Changing SotA

Until these days, enterprises used to follow a static Security Policy devoted to controlling a certain structure \cite{BYOD13}, where the Information Assets and the devices were purchased and maintained by the company. Now that corporate networks are becoming dynamic for being adapted to the BYOD philosophy, there is an additional risk because the devices that the employees use are not always company-owned. A needed security policy, or in this case, an Information Security Policy (ISP from now on) should deal with the way of protecting a certain organization's information against a security breach. Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}; an ISP is built depending on the characteristics of the community/organisation that they are built for.

On the other hand, employee-owned devices like smartphones, are not just for work purposes anymore. As the name says, smartphones are more than simple old cellular phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life. For this reason, the risk of uncontrolled devices accessing to corporate access in unsafe conditions, due to the number of risky applications is bigger.

>>>>

One of the tasks of a Chief Security Officer (CSO) is to elaborate an efficient set of Information Security Policies (ISPs), for controlling a certain, and already known, structure \cite{Opp_Security11}. This means that, until the appearance of BYOD, enterprises used to follow static security policies devoted to control an environment where the company assets and the devices were purchased and maintained by the company. Now that corporate networks are becoming dynamic for being adapted to this BYOD philosophy, there is an additional risk because the devices that the employees use are not always company owned. This means that the CSOs have to find the balance between having a fast response to any user action that might cause harm (in terms of money loss because of a security incident), and trying to avoid monitoring the users in a way that is against privacy. A needed security policy, or in this case, an ISP should deal with the way of protecting a certain organization's information against a security breach. Though there are standards, such as the ISO27002 or the Security Forum's Standard of Good Practice\footnote{\url{https://www.securityforum.org}}, and many guidelines \cite{SecPol09}, an ISP should be adapted depending on the characteristics of the community/organisation that they are built for. In this sense, MUSES stands up for a self-adaptation of the security policies of a company.

On the other hand, employee owned devices like smartphones, can be both used for personal matters at work, and for continue working outside of the workplace. As the name says, smartphones are more than simple mobile phones, and people who use them in their works have the possibility of maintaining a good balance between work and private life. For this reason, the risk of uncontrolled devices accessing to corporate assets in unsafe conditions, due to the number of new risks which are linked to smartphones \cite{gangula2013survey}, is bigger.
